From Questions to Queries – Enhancing the Curt System by a Theory and Implementation of Embedded WH-Questions

### 2008-08-30 thesis/paper.tex
Put two new papers in discussion, correct mistakes

Growing efforts have thus been made to provide a technology that is (going to
be) able to extract logical formulae from sentences of ordinary language and
establish relations between objects of their logical representation. In addition,
providing a means to compute with said representations will eventually enable
the machine-processing of an abstract concept of meaning. In doing so, the
ultimate goal may be to enable a man-made system to \emph{understand} what
humans communicate.

@@

\subsection{Comparison of the Curt System}\label{sec:comparison}

@@

@@

Today it seems that statistical question answering systems make inroads to the search market,
and some argue that they are bound to eventually supplant current document/term-based
search engines. Even though \abbr{QA} systems also operate on the domain of
answering questions, their approach to resolving them differs in most aspects
from that of dialogue systems. The latter have a much higher obligation to
correctness, since their results are typically not subject to peer
review and serve an entirely different purpose.

>>>>

As access to vast amounts of information becomes more and more ubiquitous, and
the information accessible to humans grows more diverse every day, users
struggle to find what they need among the vast amounts of data available to
them. Current search technologies aim to provide easy access to a constantly
changing pool of knowledge, yet they are hardly beyond the stage of looking for
exact text matches. Machine processing still fails to \emph{understand} the
information it has to deal with and sees data as nothing more than a set of
strings. But often a user's demands do not ask for a piece of text, but for an
abstract concept, or a relation. Knowing that natural language is most likely
infinite, such relations are virtually endless in number, and  one can only
conclude that trying to enumerate all relations between the bits of  human
knowledge in gargantuan databases is bound to be a never-ending task.

Growing efforts have thus been made to provide a technology that is (going to
be) able to extract logical formulae from sentences of ordinary language and
establish relations between objects of their logical representation. In addition,
providing a means to compute with said representations will eventually enable
the machine-processing of an abstract concept of meaning. In doing so, the
ultimate goal may be to enable a man-made system to \emph{understand} what
humans communicate. Then, these representations of knowledge could be queried, and
infer from their knowledge, what an optimal answer to a given query might be --
maybe even inventing an answer to a question never posed before along the way.

@@

\subsection{Inferencing, Question Answering, and Dialogue Systems Today}\label{sec:comparison}

@@

\cite{tenCate} present a tableaux method for resolving questions and also
propose an algorithm in \prol{} as an implementation. Their approach is a more
theoretical one, and they do not provide any particular implementation of their
work. Although their methods seems promising, to say the least, it was chosen to
avoid the implementation of a specialized inferencing system. \cite{bosgabdsil}
mention the combinatorial explosion that lurks behind the treatment of questions
and this is a considerable threat to any implementation of deep semantic
\abbr{QA} systems. By using external inferencing tools, an implementation of
the semantics of questions can focus on more essential issues than the
resolution of formulae. % too offending. fixme

Discourse Representation Theory is also used in \cite{bosgabdsil}, who present
an approach to question answering quite similar to what is presented in this
paper. In contrast to \cite{tenCate}, who use their own internal inferencing
method to resolve questions, Bos and Gabdsil also use external inferencing very
similar to the \curt{} system. Their results will be discussed later on, and
explicitly compared to the present results.

An attempt to bring inferencing to the world of \abbr{QA} systems can be found
in \cite{webber}.

@@

Today it is clear that statistical question answering systems make inroads to
the search market, and not many doubt that they are bound to eventually replace
current document/term-based search engines. Even though \abbr{QA} systems also
operate on the domain of answering questions, their approach to resolving them
differs in most aspects from that of dialogue systems. The latter have a much
higher obligation to correctness, since their results are typically not subject
to peer review and serve an entirely different purpose.
